Intro to Linear Regression

### 2018-11-20 DATA606/Intro to Linear Regression.Rmd
More work on Intro to Linear Regression

(a) Given that the average standardized beauty score is -0.0883 and average teaching evaluation score is 3.9983, calculate the slope. Alternatively, the slope may be computed using just the information provided in the model summary table.

(b) Do these data provide convincing evidence that the slope of the relationship between teaching evaluation and beauty is positive? Explain your reasoning.

(c) List the conditions required for linear regression and check if each one is satisfied for this model based on the following diagnostic plots.

>>>>

(a) Given that the average standardized beauty score is -0.0883 and average teaching evaluation score is 3.9983, calculate the slope. Alternatively, the slope may be computed using just the information provided in the model summary table. **0.1325028**

$y - y_0 = \text{slope} \times (x - x_0)$

$4.010 - 3.9983 = \text{slope} \times (0 - -0.0883)$

$0.0117 =0.0883 \times \text{slope}$

$\text{slope}=\frac{0.0117}{0.0883} = 0.1325028$

(b) Do these data provide convincing evidence that the slope of the relationship between teaching evaluation and beauty is positive? Explain your reasoning. **There is a positive slope however it is not very strong.**

(c) List the conditions required for linear regression and check if each one is satisfied for this model based on the following diagnostic plots. **Linearity: Scatterplot indicates a positive relationship but it is weak.  The slope is consistant with this.  Nomally Distributed Residuals: The Q-Q Plot indicates it.  Constant variability: The residuals scatterplot indicates this condition is met.  Independent Observations: The evaluations is independant of the other.**
